The connection between star formation rate and dark matter halo mass during reionization

### 2015-09-12 paper/ms.tex

\keywords{galaxies: high-redshift --- methods: numerical} 
\begin{abstract}
We present updated constraints on the relationship between the star
formation rate and dark matter halo mass at redshift $z\sim 6$.
The observational basis for our work is the restframe UV luminosity
function data obtained with HST, CFHTLS, Subary and UKIRT.
The constraints are based on an abundance matching methodology to the
observational data using cosmological N-body simulations assuming a
doible power law relationship between halo mass and star formation
rate follows
We take into account the influence on the results of the dust extinction
scaling derived from observations by Bouwens et al. (2012).
Taking advantage of a wide dynamical range in observations and
simulations we manage to constrain the free parameters of our model
for halos in the mass range $10^{10}\Msun < M_{h}<10^{13}\Msun$. 
We compare our results against the constraints of abundance matching
methods (to the stellar mass), a semi-analytic model of galaxy
formation (GALFORM) and a hydrodynamical simulation (Illustris).
\end{abstract}

>>>>

\keywords{galaxies: high-redshift --- methods: numerical} 
\begin{abstract}
We present updated constraints on the relationship between the star
formation rate and dark matter halo mass at redshift $z\sim 6$.
The observational basis for our work is the restframe UV luminosity
function data obtained with HST, CFHTLS, Subary and UKIRT.
The constraints are based on an abundance matching methodology to the
observational data using cosmological N-body simulations assuming a
doible power law relationship between halo mass and star formation
rate follows
We take into account the influence on the results of the dust extinction
scaling derived from observations by Bouwens et al. (2012).
Taking advantage of a wide dynamical range in observations and
simulations we manage to constrain the free parameters of our model
for halos in the mass range $10^{10}\Msun < M_{h}<10^{13}\Msun$. 
We compare our results against the constraints of abundance matching
methods (to the stellar mass), a semi-analytic model of galaxy
formation and a hydrodynamical simulation.
\end{abstract}
